---
title: "Graphing Allosensitized mice BMT data"
#output: html_notebook
---

This notebook will visualize the allosensitized mice BMT data. I wanted more customization than is easily available in excel


# Libraries
```{r}
library(ggplot2)
library(tidyverse)
```

# Read in data

Read in the data. While numbers are used for start and end dates of treatment as well as group, there are only a few values and I will treat them as factors. The only continuous values are survival, percents, and mfi values.

```{r}
data_raw <- read.csv("allo_bmt_data.csv", header = T, stringsAsFactors = T)

data_raw
```
Now I will start to change the dataset from the initial read in, so I will create a new 'data' object.

```{r}
data <- data_raw |>
  mutate(group = as.factor(group))

data
```

```{r}
p <- ggplot(data, aes(mfi_10, perc_10)) +
  geom_point(aes(color = engrafted, shape = bmt_rux_end, size = 0.05)) +
  geom_smooth() +
  labs(x = "MFI, 1:10 dilution",
       y = "% positive, 1:10 dilution",
       title = "Transplant Outcomes of Allosensitized Mice",
       subtitle = "Anti-IgG levels pre-transplant ") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  guides(size = FALSE) 

p
```


Make the same plots for 1:40 dilution and 1:160 dilutions

```{r}
q <- ggplot(data, aes(mfi_40, perc_40)) +
  geom_point(aes(color = engrafted, shape = bmt_rux_end, size = 0.05)) +
  geom_smooth() +
  labs(x = "MFI, 1:40 dilution",
       y = "% positive, 1:40 dilution",
       title = "Transplant Outcomes of Allosensitized Mice",
       subtitle = "Anti-IgG levels pre-transplant ") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  guides(size = FALSE) 

r <- ggplot(data, aes(mfi_160, perc_160)) +
  geom_point(aes(color = engrafted, shape = bmt_rux_end, size = 0.05)) +
  geom_smooth() +
  labs(x = "MFI, 1:160 dilution",
       y = "% positive, 1:160 dilution",
       title = "Transplant Outcomes of Allosensitized Mice",
       subtitle = "Anti-IgG levels pre-transplant ") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  guides(size = FALSE) 

q
r
```



Save plots

```{r}
ggsave("transplant_outcomes_1_10.png",
       plot = p,
       width = 8,
       height = 6,
       units = "in")

ggsave("transplant_outcomes_1_40.png",
       plot = q,
       width = 8,
       height = 6,
       units = "in")

ggsave("transplant_outcomes_1_160.png",
       plot = r,
       width = 8,
       height = 6,
       units = "in")
```

